### 2023-02-21 main.tex
Added notebook environments for code listings and re-organized packages again

% PACKAGE CONFIGURATIONS
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[labelfont=bf, labelsep=period]{caption}
\renewcommand{\figurename}{Fig}

\usepackage[margin=1in]{geometry}
%\usepackage{setspace}  % double spacing
%\doublespacing
\usepackage[skip=10pt]{parskip}  % Remove indents
\usepackage{titlesec}  % Modify chapter title format
\titleformat{\chapter}
    [display]% Shape (chapter label in separate paragraph)
    {\bfseries\Large}% Format
    {\MakeUppercase{\chaptertitlename} \thechapter}% Label
    {0in}% Sep
    {}% Before code
    []% After code
\setcounter{tocdepth}{1}  % Only number divisions to section

\usepackage{hyperref}
\usepackage[doi=false,url=false]{biblatex}
\addbibresource{refs.bib}

\pagestyle{plain}

% ENVIRONMENTS
\newenvironment{abstract}%  Astract environment
    {% Begin code
    \small%
    \begin{center}%
    \textbf{Abstract}%
    \end{center}%
    \quotation%
    }%
    {\par% End code
    }

@@

\chapter{Software tools and tutorials}
\input{chapter3/chapter3.tex}

@@

\chapter{Supporting information for chapter 1}
\input{chapter1/chapter1_supporting.tex}

>>>>

% PACKAGE AND ENVIRONMENT CONFIGURATIONS
\usepackage{amsmath}
\usepackage{graphicx}

% Code listings
\usepackage[outputdir=out]{minted}
\usepackage{tcolorbox}
\usepackage{lmodern}

% Margins and spacing
\usepackage[margin=1in]{geometry}
%\usepackage{setspace}  % double spacing
%\doublespacing
\usepackage[skip=10pt]{parskip}  % Remove indents
\pagestyle{plain}

% Chapter and figure formatting
\usepackage{titlesec}  % Modify chapter title format
\titleformat{\chapter}[display]% Shape (chapter label in separate paragraph)
                      {\bfseries\Large}% Format
                      {\MakeUppercase{\chaptertitlename} \thechapter}% Label
                      {0in}% Sep
                      {}% Before code
                      []% After code
\setcounter{tocdepth}{1}  % Only number divisions to section
\usepackage[labelfont=bf, labelsep=period]{caption}
\renewcommand{\figurename}{Fig}

% References
\usepackage[doi=false,url=false]{biblatex}
\addbibresource{refs.bib}
\usepackage{hyperref}

% ENVIRONMENTS
\newenvironment{abstract}
{% Begin code
 \small
 \begin{center}
 \textbf{Abstract}
 \end{center}
 \quotation
}
{% End code
}

\definecolor{incolor}{RGB}{51,63,153}
\definecolor{outcolor}{RGB}{200,78,41}
\definecolor{bgcolor}{RGB}{247,247,247}

\newlength{\promptwidth}
\setlength{\promptwidth}{0.5in}

\newcommand{\prompt}[2]
{\makebox[0pt][r]{\texttt{\color{#2}#1:\ }}\vspace{-\baselineskip}}

\newenvironment
{NotebookIn}
{
 \VerbatimEnvironment
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=bgcolor,
                   left skip=\promptwidth,
                   title=\prompt{In}{incolor},
                   attach title to upper]
 \begin{minted}{python}
}
{
 \end{minted}
 \end{tcolorbox}
}

\newenvironment
{NotebookOut}
{
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=white,
                   left skip=\promptwidth,
                   title=\prompt{Out}{outcolor},
                   attach title to upper]
 \\ \ttfamily
}
{
 \end{tcolorbox}
}

\newenvironment
{NotebookImage}
{
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=white,
                   left skip=\promptwidth,
                   title=\prompt{Out}{outcolor},
                   attach title to upper]
 \\
}
{
 \end{tcolorbox}
}

@@

\chapter{Software tools and tutorials}
\graphicspath{{chapter3/}}
\input{chapter3/chapter3.tex}

@@

\chapter{Supporting information for chapter 1}
\graphicspath{{chapter1/figures/}}
\input{chapter1/chapter1_supporting.tex}
